Untitled

### 2024-07-17 compare/compare.qmd
fits->ecsv for simplicity

```{python}
import numpy as np
import matplotlib.pyplot as plt
from sklearn.metrics import r2_score
from astropy.io import fits
from astropy.coordinates import SkyCoord
from astropy.table import Table, join, QTable
import astropy.units as u
from astropy.visualization import quantity_support
import glob
import os

hdul = fits.open("../tables/inner_join.fits")
print(hdul[1])
```

```{python}
print("jell
```

>>>>

```{python}
import numpy as np
import matplotlib.pyplot as plt
from sklearn.metrics import r2_score
from astropy.io import ascii
from astropy.coordinates import SkyCoord
from astropy.table import Table, join, QTable
import astropy.units as u
from astropy.visualization import quantity_support
import glob
import os

dt = QTable(ascii.read("../tables/inner_join.ecsv"), masked=True)
dt.info()
```

```{python}
```
